Inferring the effective start dates of non-pharmaceutical interventions during COVID-19 outbreaks

### 2020-05-19 ms/ms.tex
added ppc figures

\usepackage{amssymb,amsmath,amsthm}
\usepackage{commath}
\usepackage{longtable}
\usepackage[hyphens]{url}
\usepackage[dvipsnames]{xcolor}
\usepackage[unicode=true,colorlinks=true,urlcolor=Blue,citecolor=black,linkcolor=black]{hyperref}
\def\equationautorefname~#1\null{Eq.~(#1)\null}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage{authblk}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage{titlesec}	
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{enumitem}
\usepackage{soul}
\usepackage{booktabs}
\usepackage{pgfplotstable} % http://mirrors.ctan.org/graphics/pgf/contrib/pgfplots/doc/pgfplotstable.pdf
\usepackage{subcaption}
\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\ccell[1]{\multicolumn{1}{c}{#1}} % a wild guess...
\usepackage{adjustbox}

@@

>>>>

\usepackage{amssymb,amsmath,amsthm}
\usepackage{commath}
\usepackage{longtable}
\usepackage[hyphens]{url}
\usepackage[dvipsnames]{xcolor}
\usepackage[unicode=true,colorlinks=true,urlcolor=Blue,citecolor=black,linkcolor=black]{hyperref}
\def\equationautorefname~#1\null{Eq.~(#1)\null}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage{authblk}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage{titlesec}	
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{enumitem}
\usepackage{soul}
\usepackage{booktabs}
\usepackage{pgfplotstable} % http://mirrors.ctan.org/graphics/pgf/contrib/pgfplots/doc/pgfplotstable.pdf
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat=empty}
\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\ccell[1]{\multicolumn{1}{c}{#1}} % a wild guess...
\usepackage{adjustbox}

@@

%%% Fig PPC %%%
\begin{figure}[h]
    \centering
	\subcaption{Austria}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Austria_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Austria_ppc.pdf}
    \end{subfigure}
    %%%
	\subcaption{Belgium}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Belgium_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Belgium_ppc.pdf}
    \end{subfigure}
    %%%
	\subcaption{Denmark}    
     \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Denmark_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Denmark_ppc.pdf}
    \end{subfigure}
\end{figure}
    %%%
\begin{figure}
    \ContinuedFloat 
	\subcaption{France}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/France_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/France_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Germany}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Germany_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Germany_ppc.pdf}
    \end{subfigure}
    %%% 
	\subcaption{Italy}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Italy_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Italy_ppc.pdf}
    \end{subfigure}
    %%% 
	\subcaption{Norway}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Norway_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Norway_ppc.pdf}
    \end{subfigure}
\end{figure}
    %%%
\begin{figure}
    \ContinuedFloat   
	\subcaption{Spain}     
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Spain_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Spain_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Sweden}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Sweden_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Sweden_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{Switzerland}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Switzerland_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/Switzerland_ppc.pdf}
    \end{subfigure}
    %%%  
	\subcaption{United Kingdom}    
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/fixed/United_Kingdom_ppc.pdf}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{../figures/ppc/free/United_Kingdom_ppc.pdf}
    \end{subfigure}
    %%%
    \caption{
     \textbf{Figure S1. Posterior predictive plots.}
	}
	\label{fig:ppc}
\end{figure}

\pagebreak
